---
title: "Penguins!"
author: "Lucy D'Agostino McGowan"
output: html_document
---

## Introduction

We are interested in the relationship between flipper length and bill length for different penguin species. 

### Packages

We will use the **tidyverse** package for data wrangling, the **palmerpenguins** package to obtain the data, and the **DT** package for interactive display of tabular output.

```{r}
#| label: load-packages
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
library(DT)
```


### Data

These data were collected and made available by Dr. Kristen Gorman and the Palmer Station, Antarctica LTER, a member of the Long Term Ecological Research Network. The dataset can be accessed after loading the **palmerpenguins** package.

## Palmer Penguins

```{r}
#| label: plot

ggplot(penguins, 
       mapping = aes(x = flipper_length_mm, y = bill_length_mm, color = species)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "Flipper and bill length",
    subtitle = "Dimensions for Adelie, Chinstrap, and Gentoo Penguins at Palmer Station LTER",
    x = "Flipper length (mm)",
    y = "Bill length (mm)"
  )
```

## References

1. Horst AM, Hill AP, Gorman KB (2020). palmerpenguins: Palmer
Archipelago (Antarctica) penguin data. R package version 0.1.0.
https://allisonhorst.github.io/palmerpenguins/

## Appendix 

Below is the full dataset:

```{r}
#| label: data
#| echo: false
penguins %>% 
  datatable()
```